### 2019-03-17 paper.tex
added belief revision semantics

\usepackage[backend=biber,authordate,
ibidtracker=context,natbib,doi=false,isbn=false,url=false]{biblatex-chicago}
\addbibresource{/home/gilbert/Documents/bibliography/references.bib}

@@

\section{Belief Revision, Non-monotonic Logic, and Rational Choice}
Belief revision if the form of the most prominent AGM \parencite{alchourron85_logic_theor_chang} defines criteria for a rational agent on how to update her
beliefs when learning evidence. Crucially, this evidence might be conflicting
with what the agent already beliefs. For example, you are about to pay your bill
at a restaurant and, to your great surprise, there is no money in your wallet
\parencite[p.~48]{gaerdenfors88_knowl}.

@@

Let us look then at the revision function from a sentence \(A\) and a belief set \(K\), denoted \(K^*A\). What constitutes a rational revision? Following Quine`s `maxim of minimum mutilation' \parencite[p.~72]{rott01_chang_choic_infer}, the central postulates for belief revision aim at conserving as much as possible from \(K\) in the new set \(K^*A\) while incorporating the new evidence \(A\).\textcite{gaerdenfors88_knowl} describes six basic, minimal or elementary postulates, and two additional ones. In the interest of brevity, I will skip listing them and refer to the numerous publications agreeing on these principles, e.g. \textcite[p.~57]{gaerdenfors88_knowl, brewka97_nonmon}, \textcite{hansson17_logic_belief_revis}. As an example, this postulates states the success of the revision:

\begin{align}
  \label{eq:k2}
  \tag{(K^*2)} 
  A \in K^*A
\end{align}

\begin{equation}
  \nonumber
  \label{eq:k2}
  \tag{(K^*2)} 
  A \in K^*A
\end{equation}
The postulates are designed are designed to be intuitive and confirm to common sense (Cite). Importantly, they constrain the set of rational revision functions by way of logical (set-theoretical) considerations, but do not necessarily determine a revision uniquely \parencite[p.~53]{gaerdenfors88_knowl}.

\section{Erik Olsson's Critique}
\section{Discussion and Conclusion}
\nocite{rott01_chang_choic_infer,olsson03_belief_revis_ration_choic_unity_reason,gaerdenfors88_knowl,gaerdenfors94_nonmon_infer_based_expec,alchourron85_logic_theor_chang,makinson91_relat,sen93_inter_consis_choic,kraus90_nonmon_reason_prefer_model_cumul_logic,hansson17_logic_belief_revis, ortner11_mechan_induc,brewka97_nonmon}
\printbibliography
\end{document}

>>>>

\usepackage{amsmath}
\usepackage{ptolemaicastronomy}
\usepackage[backend=biber,authordate,
ibidtracker=context,natbib,doi=false,isbn=false,url=false]{biblatex-chicago}

\addbibresource{/home/gilbert/Documents/bibliography/references.bib}

@@

\section{Belief Revision, Non-monotonic Logic, and Rational Choice}

\subsection{Belief Revision}
Belief revision if the form of the most prominent AGM
\parencite{alchourron85_logic_theor_chang} defines criteria for a rational agent
on how to update her beliefs when learning evidence. Crucially, this evidence
might be conflicting with what the agent already beliefs. For example, you are
about to pay your bill at a restaurant and, to your great surprise, there is no
money in your wallet \parencite[p.~48]{gaerdenfors88_knowl}.

@@

Let us look then at the revision function from a sentence \(A\) and a belief set
\(K\), denoted \(K^*A\). What constitutes a rational revision? Following Quine`s
`maxim of minimum mutilation' \parencite[p.~72]{rott01_chang_choic_infer}, the
central postulates for belief revision aim at conserving as much as possible
from \(K\) in the new set \(K^*A\) while incorporating the new evidence
\(A\). \textcite{gaerdenfors88_knowl} describes six basic (minimal, elementary)
postulates, and two additional ones. In the interest of brevity, I will skip
listing them and refer to the numerous publications on these principles, e.g.
\textcite[p.~57]{gaerdenfors88_knowl, brewka97_nonmon},
\textcite{hansson17_logic_belief_revis}. As an example, the following postulates
states the success of a revision operation:
\[
    \label{eq:k2}
    \tag{$K^*2$} A \in K^*A
\]
This is supposed to prescribe that a rational revision operator always includes
the new belief in the belief set after updating. In General, the postulates are
designed to be intuitive and confirm to common sense (Cite). Importantly, the
postulates constrain the set of rational revision functions by way of logical
(set-theoretical) considerations, but do not necessarily determine a revision
uniquely \parencite[p.~53]{gaerdenfors88_knowl}.

To see this, let's consider an example. Suppose you believe that penguins are
birds, that birds fly, but penguins don't. We might represent the belief set as
\(K = Cn(\{ p \rightarrow b, b \rightarrow f, p \rightarrow \neg
f\})\),\footnote{Glancing over the fact that the beliefs are quantificational in
  nature. For the present purposes, the beliefs may be assumed to be about
  individuals, and that we have many such beliefs.} where \(Cn\) denotes a
classical consequence closure operator. We now learn that \(p\), i.e. that
Tweety is in fact a penguin. It is clear that when Tweety is a penguin, it can't
fly, even though it's a bird. The result of adding \(p\) to \(K\) is
inconsistent, so \(K\) has to be revised. How does the revised belief set
\(K^*p\) look like?

By the success postulate, we cannot drop \(p\). Since \(b \rightarrow f\) can be
assumed to be analytic, we won't drop that, either. Dropping either $b \rightarrow
f$ or $p \rightarrow \neg f$ leads to a revision satisfying postulates $K^*1 -
K^*8$. To decide between the two options in our formalism, we need additional
structure. There are a host of different such structures developed, prominently
a procedure called \emph{partial meet contraction}
\parencite[p.~80]{gaerdenfors88_knowl} and a notion called
\emph{epistemic entrenchment} \parencite[p.~86]{gaerdenfors88_knowl}. Both
are relational structures designed to prescribe a choice. Partial meet
contraction introduces a relation on maximal subsets of $K$ which don't  
imply $p$, while epistemic entrenchment orders sentences in K. To facilitate an
intuitive notion, I present a third `semantics' based on a sphere system by
\textcite{grove88_two_model_theor_chang} (also cf. \textcite[p.~83]{gaerdenfors88_knowl})

We define a set $W$ of possible worlds (which can be seen as maximal consistent
subsets of $\mathcal{L}$) organized into a set of concentric spheres $\mathcal{S}$ totally
ordered by $\subseteq$, such that $[K] = \{w \in W: w \models A \text{ for all } A \in
K\}$ is the minimal and $W$ the maximal element of $\mathcal{S}$.

Intuitively, the spheres rank the possible worlds by plausibility or normality,
with $K$, the belief set, ranked most plausible. Since $p$ is incompatible with
$K$, we have $[p] \cap [K] = \emptyset$. The idea is to revise $[K]$ such that
is only contains the most normal worlds satisfying $p$, i.e. worlds in the
$\subseteq$-minimal sphere \emph{and} in $[p]$. Compare Figure
\ref{fig:spheres1}, where $[K^*p] = S_1 \cap [p]$, such that $i \in [K^*p]$.

\begin{figure}[ht]
    \centering
    \label{fig:spheres1}
    \begin{tikzpicture}[scale=1]
        % wider layers, pointier propositions
        \tikzset{layerwidth=1,innerfactor=0,
          proposition/.style={smooth,tension=1}}
        % fill the areas between three props and their innermost spheres
        % \sphereintersect{3}{\propositionplot{30}{3.3}{30}{4}}
        \sphereintersect{2}{\propositionplot{30}{2.3}{45}{4}}
        % \sphereintersect{1}{\propositionplot{30}{1.3}{60}{4}} draw the sphere
        % system
        \spheresystem[solid]{3}
        % draw the propositions \draw \propositionplot{30}{3.3}{30}{4};
        \draw \propositionplot{30}{2.3}{45}{4};
        % \draw \propositionplot{30}{1.3}{60}{4}; draw \psi (coordinates figured
        % out by trial and error) \draw plot[smooth,tension=1.2] coordinates
        % {(-1.5,3) (1.2,-1) (.8,2.3) (2.8,.7) (3,4)}; draw and label the center
        % world, spheres, and propositions
        % \filldraw circle[radius=.05];
        \node at (0,0) {$[K]$};

        \spherepos[fill]{30}{2.2}{circle[radius=.1]}
        \spherepos[fill]{22}{2.3}{node {$i$}}
        % \spherepos{-70}{1.8}{node {$S_1$}}
        \spherepos{-70}{2.8}{node{$S_1$}}
        \spherepos{-70}{3.8}{node {$S_2$}}
        % \spherepos{4}{4.3}{node {$\phi_1$} node at +(0,.5) {$\phi_2$} node at
        %   +(0,1) {$\phi_3$}}
        \spherepos{4}{4.3}{node at +(0,.5) {$[p]$}}
        % \spherepos{80}{4}{node {$\psi$}}
    \end{tikzpicture}

    \caption{Belief set $K$ in a system of spheres.}
\end{figure}

How does this help with choosing between dropping $b \rightarrow
f$ or $p \rightarrow \neg f$? Depending on the agent's sphere system, either $i
\models p \land b \land f$ or $i \models p \land b \land \neg f$. Intuitively,
either the agent finds it more plausible that penguins fly or they
don't.\footnote{Note to self: what if $i_1 \models p \land f$ and $\i_2 \models
  p \land \neg f$, $i_1,i_2 \in K^*p$?} With the help of this additional
structure, then, we can model the example as we please.

\subsection{Non-monotonic Logic: Preferential Semantics}
\section{Erik Olsson's Critique}
\section{Discussion and Conclusion}
\nocite{rott01_chang_choic_infer,olsson03_belief_revis_ration_choic_unity_reason,gaerdenfors88_knowl,gaerdenfors94_nonmon_infer_based_expec,alchourron85_logic_theor_chang,makinson91_relat,sen93_inter_consis_choic,kraus90_nonmon_reason_prefer_model_cumul_logic,hansson17_logic_belief_revis,
  ortner11_mechan_induc,brewka97_nonmon} \printbibliography
\end{document}
